PM Mungbean meta-analysis

### 2021-02-02 02_Preliminary_analysis.Rmd
spelling

### Fungicide Doses{#fungicide-doses}  
This analysis focuses only the DMI fungicides, tebuconazole and propiconazole, which were trialed the most often.

>>>>

### Fungicide Doses{#fungicide-doses}  
This analysis focuses only the DMI fungicides, tebuconazole and propiconazole, which were trialled the most often.
